Functional vs. Object Oriented Programming: Productivity comparison

### 2015-10-23 article.tex
method changed

>>>>

Static code analysis on the set of algorithms described below has been performed using the command line tool called Count Lines of Code (cloc) \cite{cloc}, which counts lines of code, blank lines and comments in multiple languages. There are several options on how to present the data using this tool, i.e. one can obtain an analysis of a language used inside a project (several files), or extract results for each file individuals etc.
